\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=0.75in, top=0.65in, bottom=0.65in}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

% ─── Colors ──────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{26,115,232}
\definecolor{dark}{RGB}{32,33,36}
\definecolor{light}{RGB}{95,99,104}

% ─── Helpers ─────────────────────────────────────────────────────────────────
\newcommand{\github}[1]{\href{https://github.com/#1}{\texttt{github.com/#1}}}
\newcommand{\linkedin}[1]{\href{https://linkedin.com/in/#1}{\texttt{linkedin.com/in/#1}}}
\setlist{noitemsep, topsep=2pt, partopsep=0pt, parsep=0pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

% ═══════════════════════════════════════════════════════════════════════════════
% HEADER
% ═══════════════════════════════════════════════════════════════════════════════
{\fontsize{22}{26}\selectfont\textbf{Asmi Yadav}}\par
\vspace{4pt}
{\fontsize{10}{13}\selectfont
\textcolor{light}{+91 99931 00849  $\cdot$  asmiyadav2004@gmail.com  $\cdot$
\linkedin{asmi-yadav-b0824724a}  $\cdot$  \github{neuralasmi}}
}\par
\vspace{6pt}
{\color{accent}\hrule height 1.2pt}\par
\vspace{6pt}

% ═══════════════════════════════════════════════════════════════════════════════
% ABOUT
% ═══════════════════════════════════════════════════════════════════════════════
\section*{About Me}
Fourth-year BTech student in Computer Science (IoT \& Intelligent Systems) at
Manipal University Jaipur, graduating August 2026. Passionate about building
production-ready ML systems. Seeking ML engineering internships to apply deep
learning, NLP, and MLOps skills at the intersection of research and deployment.

% ═══════════════════════════════════════════════════════════════════════════════
% EDUCATION
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Education}
\textbf{Manipal University Jaipur} \hfill Aug 2022 -- Aug 2026 \\
\textit{B.Tech Computer Science (IoT \& Intelligent Systems)} \hfill Jaipur, Rajasthan \\[6pt]
\textbf{St. Joseph's Coed Sr. Sec. School, Bhopal} \\
CBSE 12th Boards -- 91.3\% \hfill Mar 2021 -- Mar 2022 \\
CBSE 10th Boards -- 82\% \hfill Mar 2019 -- Mar 2020

% ═══════════════════════════════════════════════════════════════════════════════
% EXPERIENCE
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Experience}

\textbf{FRND} -- \textit{AI Content Analyst (Intern)} \hfill Jan 2026 -- Feb 2026
\begin{itemize}
  \item Analyzed large-scale conversational datasets to identify response gaps,
        repetition patterns, and model inconsistencies, improving chatbot quality.
  \item Contributed to training data refinement using Python, HuggingFace
        Transformers, and Scikit-learn in the NLP optimization pipeline.
  \item Gained hands-on exposure to end-to-end AI model training workflows,
        applying ML knowledge to real-world production systems.
\end{itemize}

\textbf{Freelance -- Tiffinly} -- \textit{Community Meal Marketplace} \hfill Apr 2025 -- Sept 2025
\begin{itemize}
  \item Built MVP for affordable meal marketplace connecting college students with
        local home cooks; ran pilot with 50 students and 10 cooks.
  \item Features: meal request posting, nearby cook matching, REST API data
        handling, in-app chat for price/timing negotiation.
\end{itemize}

% ═══════════════════════════════════════════════════════════════════════════════
% TECHNICAL SKILLS
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Technical Skills}
\textbf{Languages:} Python, Java, C, C++, HTML/CSS, SQL \\
\textbf{ML/AI:} Scikit-learn, HuggingFace Transformers, Pandas, NumPy,
  Matplotlib, Seaborn, PyTorch, XGBoost \\
\textbf{Databases:} MongoDB, PyMongo, MySQL \\
\textbf{Tools:} VS Code, Git, Postman, Jira, Weights \& Biases, MLflow, Docker, FastAPI

% ═══════════════════════════════════════════════════════════════════════════════
% ML PROJECTS
% ═══════════════════════════════════════════════════════════════════════════════
\section*{ML Projects (github.com/neuralasmi)}

% ── 1 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{1. Titanic Survival Prediction}
\hfill \github{neuralasmi/project-1-titanic-ml} \\
\textit{Logistic Regression, Random Forest, XGBoost} --
Full ML pipeline on Kaggle Titanic (891 passengers, 8 engineered features).
5-fold stratified CV. Best: XGBoost -- 82.1\% accuracy, 0.868 ROC-AUC on holdout.
Pipeline: EDA $\rightarrow$ preprocessing $\rightarrow$ feature engineering
$\rightarrow$ GridSearchCV $\rightarrow$ evaluation.

% ── 2 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{2. House Price Prediction}
\hfill \github{neuralasmi/project-2-house-prices} \\
\textit{Ridge, Lasso, ElasticNet, PolynomialFeatures} --
Regression on Kaggle House Prices. Log-transform target, StandardScaler,
PolynomialFeatures (degree=2) for interaction terms. 70/15/15 split.
Best: ElasticNet, Val RMSE $\approx$ 0.14 (log), R$^2$ $\approx$ 0.87.

% ── 3 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{3. Customer Churn Prediction}
\hfill \github{neuralasmi/project-3-churn-ml} \\
\textit{Random Forest, Gradient Boosting, SMOTE, Imbalanced Data} --
Imbalanced classification (10k records, $\sim$26\% churn rate).
class\_weight='balanced' + optional SMOTE. Metrics: AUC-ROC, F1,
confusion matrix, precision-recall curve, Youden's J threshold tuning.

% ── 4 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{4. Spam Email Classifier}
\hfill \github{neuralasmi/project-4-spam-classifier} \\
\textit{TF-IDF, Naive Bayes, Logistic Regression, NLP} --
NLP pipeline: lowercase, stopword removal, TF-IDF with unigrams+bigrams (1,2).
Models: MultinomialNB and Logistic Regression.
Evaluated on accuracy, precision, recall, F1.

% ── 5 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{5. MNIST Digit Classifier}
\hfill \github{neuralasmi/project-5-mnist-cnn} \\
\textit{PyTorch CNN, 28$\times$28 grayscale} --
Custom CNN from scratch: 2 conv blocks (32$\rightarrow$64 channels) + FC 3136$\rightarrow$128$\rightarrow$10.
Auto-downloads MNIST. Checkpointing on best accuracy,
DataLoader with num\_workers=4.

% ── 6 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{6. CIFAR-10 Image Classification}
\hfill \github{neuralasmi/project-6-cifar10-cnn} \\
\textit{VGG-style, ResNet, Data Augmentation, WandB, CosineAnnealing} --
VGG-style (5 conv blocks) and ResNet (residual connections) for CIFAR-10.
Data augmentation: RandomHorizontalFlip, RandomCrop+padding, ColorJitter.
SGD + CosineAnnealing LR + early stopping. Weights \& Biases tracking.
Comparison runs: with vs without augmentation.

% ── 7 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{7. Named Entity Recognition (BERT)}
\hfill \github{neuralasmi/project-7-ner-bert} \\
\textit{bert-base-uncased, HuggingFace, CoNLL-2003, token classification} --
Fine-tuned bert-base-uncased on CoNLL-2003. Word-to-subword label alignment
(-100 for special tokens). 3 epochs, batch 16, lr 5e-5.
Entity-level F1 via seqeval. Entity types: PER, ORG, LOC, MISC.

% ── 8 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{8. Movie Recommender System}
\hfill \github{neuralasmi/project-8-recommender} \\
\textit{SVD, Collaborative Filtering, FastAPI, MovieLens 1M} --
SVD matrix factorization on MovieLens 1M. Top-K personalized recommendations.
Evaluation: RMSE and Hit Rate@K. FastAPI REST API:
/health, /recommend/\{user\_id\}, /movie/\{movie\_id\}.

% ── 9 ────────────────────────────────────────────────────────────────────────
\noindent\textbf{9. FastAPI + Docker ML Serving}
\hfill \github{neuralasmi/project-9-fastapi-docker} \\
\textit{FastAPI, Docker, scikit-learn, RandomForest} --
Containerized ML model serving. RandomForest on Iris dataset.
Endpoints: GET /health, POST /predict. Docker (python:3.11-slim).
Separates train\_model.py from main.py API serving.

% ── 10 ───────────────────────────────────────────────────────────────────────
\noindent\textbf{10. MLflow Pipeline Automation}
\hfill \github{neuralasmi/project-10-mlflow-pipeline} \\
\textit{MLflow, experiment tracking, model registry, batch inference} --
MLflow tracking: parameters, metrics, artifacts. Random Forest vs Gradient
Boosting comparison. Registered model workflow. CLI args: --lr, --epochs,
--model, --compare, --register, --inference.

% ═══════════════════════════════════════════════════════════════════════════════
% CERTIFICATIONS
% ═══════════════════════════════════════════════════════════════════════════════
\section*{Certifications}
\begin{itemize}
  \item \textbf{Mastering Data Structures and Algorithms (C/C++)} --
        Abdul Bari (ID: 1000056968) -- fundamental to advanced DSA with
        implementation and algorithm analysis emphasis.
  \item \textbf{AI Tools and ChatGPT Workshop} -- real-world AI tools for
        content creation, data handling, and productivity.
\end{itemize}

\end{document}
